Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-12 programming23/paper.tex
blackbox, sec 3 end para, redundancies

To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large and
imprecise edit ranges, for example, if the user edits at the beginning and end
of the file.
We acknowledge this and other threats in~\cref{s:threats}.
The upshot of this strategy is that it reduces the size and complexity of
telemetry records because there is only one interval for errors to overlap with.

@@

The counts are imprecise because of telemetry granularity.
If a creator removes one error but then
introduces another on a different line, this can manifest as
a keep (\keepsym{}) rather than one add (\addsym{)} and one drop (\dropsym{}).

@@

Second, the edit ranges are a coarse approximation of actual edits.
They begin at the lowest edited line of code and end at the highest
edited line, even if nothing between those lines changed.

@@

There is a rich body of work that uses IDE instrumentation to study programmers
(e.g.,~\cite{pgnwk-koli-2022,wk-icer-2019,hl-icse-2010,j-ieeesoft-2013,kje-ase-2010, mmlb-swvis-2014, ncvjd-ecoop-2013, rl-icse-2008, we-xp-2004}).
WatchDog records the time that programmers spend reading, writing, and testing
code~\cite{blpgz-icse-2016}.
TDD-Guide collects similar data to teach testing methods~\cite{mdk-xp-2008}.
The Blackbox project collects Java programs and has enabled
dozens of contributions to the area of CS education~\cite{bask-icer-2018,bkmu-sigcse-2014}.
Other logging-based studies of Java programs draw conclusions from compiler error
messages~\cite{bgimgm-cse-2016,dlc-iticse-2014}.
The GRUMPS telemetry system collected 4.7 million keystroke-level actions from
Ada learners~\cite{tkdmceg-ascilite-2003,tm-iticse-2004}.
None of the above are sufficiently private to work for Roblox Studio.
The BitFit project counts notable events (compile program, ask for hint, etc.)
for Java~\cite{ekc-wccce-2016,anna-russo-kennedy-ms-2006}.
While it does operate in a transparent~\cite{transparent-telemetry} manner, it
only provides coarse-grained information that would be insufficient in our
study.

>>>>

To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large and
imprecise edit ranges, for example, if the user edits at the beginning and end
of the file.
The upshot of this strategy is that it reduces the size and complexity of
telemetry records because there is only one interval for errors to overlap with.

This telemetry design is admittedly coarse-grained.
For instance, it does not distinguish between edits that remove one error
while introducing another.
We acknowledge this and other threats in~\cref{s:threats}.
The main advantages of this telemetry are the small size of each record and
the complete lack of private information.
Furthermore, despite the limitations, this telemetry supports a variety of
inferences that we showcase in the next section.

@@

@@

Second, the edit ranges are a coarse approximation of actual edits.
They begin at the lowest edited line of code and end at the highest
edited line, even if nothing between those lines changed.
On a related note, the computatation that determines whether an old
type error overlaps with the current edit range has many edge cases,
especially to handle deletions, and may mis-count.
This could explain why~\cref{t:type-error-survival} reports zero syntax errors
that overlap with the current edit range; if the fix is to delete code,
then the edit range is empty.

@@

There is a rich body of work that uses IDE instrumentation to study programmers
(e.g.,~\cite{pgnwk-koli-2022,wk-icer-2019,hl-icse-2010,j-ieeesoft-2013,kje-ase-2010, mmlb-swvis-2014, ncvjd-ecoop-2013, rl-icse-2008, we-xp-2004,bgimgm-cse-2016,dlc-iticse-2014}).
The Blackbox project has accumulated terabytes of Java code over a ten-year span,
and has thereby enabled dozens of contributions to CS education~\cite{bask-icer-2018,bkmu-sigcse-2014}.
The GRUMPS telemetry system collected over four million keystroke-level actions to study
student programmers~\cite{tkdmceg-ascilite-2003,tm-iticse-2004}.
WatchDog records the time that programmers spend reading, writing, and testing
code~\cite{blpgz-icse-2016}.
TDD-Guide collects similar data to teach testing methods~\cite{mdk-xp-2008}.
None of the above are sufficiently private to work for Roblox Studio.
The BitFit project counts notable events (compile program, ask for hint, etc.)
for Java~\cite{ekc-wccce-2016,anna-russo-kennedy-ms-2006}.
While it does operate in a transparent~\cite{transparent-telemetry} manner, it
provides only coarse-grained information that would be insufficient in our
study.
